Death By Dropdown?

### 2025-03-25 conference-materials/2025_shiny-conf/slides.qmd
Updated Slides and added Images/screenshots for hands-on code examples

::: {.column width="40%"}
![](https://media.giphy.com/media/v1.Y2lkPTc5MGI3NjExMzhmY2YwMDA5MWFjOTlmN2Y0MGE2YjQzNmI5YTEzZDE3MWE1ZDIwNSZlcD12MV9pbnRlcm5hbF9naWZ5X2dpZiZjdD1n/32mC2kXYWCsg0/giphy.gif)
:::
::::

@@

::: {.nonincremental}
1. **Notice** the Problem
2. **Interpret** the User's Need
3. **Structure** the Dashboard
4. **Anticipate** User Behavior
5. **Validate** & Empower the User
:::

> _(placeholder for BID framework visual)_

@@

::: {.r-fit-text}
Hands-on example using `{reactable}` + `{echarts4r}` to implement Stages 1–5
:::

> _(placeholder for staged code walkthrough or animated screen recording)_

>>>>

::: {.column width="40%"}
![](https://media0.giphy.com/media/v1.Y2lkPTc5MGI3NjExbzVhM3d3MjJvYTNyc3puM2E0cmduZjFweXhrczNwcXI0b3FhN203aCZlcD12MV9pbnRlcm5hbF9naWZfYnlfaWQmY3Q9Zw/l44Q5OXJ6qaNr838Q/giphy.gif)
:::
::::

@@

::: {.column width="60%"}
::: {.nonincremental}
1. **Notice** the Problem
2. **Interpret** the User's Need
3. **Structure** the Dashboard
4. **Anticipate** User Behavior
5. **Validate** & Empower the User
:::
:::

::: {.column width="40%"}
![The BID Framework](The_BID_framework.png)
:::

@@

::: {.r-fit-text}
Hands-on example using `{reactable}` to implement Stages 1–3
:::

::: {.r-stack}
![Example Stages 1-3](Screenshot_examples_main_1.png){width="50%"}

![Example Stages 1-3](Screenshot_examples_main_2.png){.fragment width="50%"}

![Example Stages 1-3](Screenshot_examples_main_3.png){.fragment width="50%"}

![Example Stages 1-3](Screenshot_examples_main_4.png){.fragment width="50%"}
:::

## Implementation Demo {.scrollable background-color="#F9F9F9"}

::: {.r-fit-text}
Hands-on example using `{reactable}` to implement Stages 1–3
:::

![Example Stages 1-3](code_example_bar_graph_full.png){height="100%"}

::: {.r-fit-text}
Hands-on example using `{echarts4r}` to implement Stages 4 & 5
:::

::: {.r-stack}
![Example Stages 4 & 5](Screenshot_examples_Deep_Dives_1.png){width="50%"}

![Example Stages 4 & 5](Screenshot_examples_Deep_Dives_2.png){.fragment width="50%"}

![Example Stages 4 & 5](Screenshot_examples_Deep_Dives_3.png){.fragment width="50%"}
:::

::: {.r-fit-text}
Hands-on example using `{echarts4r}` to implement Stages 4&5
:::

> Placeholder for code example
